Topological approach to finding blackholes in directed networks

### 2019-12-08 blackholes/pavt/sketch.tex
Small updates

>>>>

\begin{table}[]
	\caption{Configuration of experimental graphs}
	\label{tabular:graphs}
	\begin{center}
		\begin{tabular}{c|c|c}
			Graph Type & Nodes Count & Edges Count \\
			\hline
			RMAT.04 & 16 & 177 \\
			RMAT.06 & 64 & 1270 \\
			RMAT.08 & 256 & 6663 \\
			RMAT.10 & 1024 & 30186 \\
			RMAT.12 & 4096 & 126988 \\
			RMAT.14 & 16384 & 517554 \\
			RMAT.16 & 65536 & 2087072 \\
			RMAT.18 & 262144 & 7892410 \\
			RMAT.20 & 1048576 & 32993233 \\
			RMAT.22 & 4194304 & 67099679 \\
			SSCA2.04 & 16 & 120 \\
			SSCA2.06 & 64 & 722 \\
			SSCA2.08 & 256 & 2668 \\
			SSCA2.10 & 1024 & 10529 \\
			SSCA2.12 & 4096 & 43603 \\
			SSCA2.14 & 16384 & 173477 \\
			SSCA2.16 & 65536 & 677649 \\
			SSCA2.18 & 262144 & 2724762 \\
			SSCA2.20 & 1048576 & 10902287 \\
			SSCA2.22 & 4194304 & 43580024 \\
			UR.04 & 16 & 207 \\
			UR.06 & 64 & 1614 \\
			UR.08 & 256 & 7652 \\
			UR.10 & 1024 & 32201 \\
			UR.12 & 4096 & 130486 \\
			UR.14 & 16384 & 523740 \\
			UR.16 & 65536 & 2096570 \\
			UR.18 & 262144 & 8388074 \\
			UR.20 & 1048576 & 33553908 \\
			UR.22 & 4194304 & 134217174
		\end{tabular}
	\end{center}
\end{table}

 In order to save time,
the algorithms did not print out found blackholes, but printed counter on every found and not filtered (by any reason) blackhole.

Please, mention, that "blackhole found" means that we have a set of vertex numbers in memory ready to be printed out and it's already validated.
